\documentclass{article}[14pt]
\usepackage[utf8]{inputenc}
\usepackage{tikz,lipsum,lmodern}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[margin=2.5cm]{geometry}
\usepackage{fontawesome} % ICONS: http://ctan.math.illinois.edu/fonts/fontawesome/doc/fontawesome.pdf
\usepackage{amssymb}

\setlength\parindent{0pt}

\NewDocumentCommand{\colorrule}{O{.4pt}m}{%
}

\newcommand{\skill}[1]{
  \hfill
  \foreach \n in {1,...,#1}{{\normalsize$\bullet$\hspace{1pt}}}
  \vspace{4pt}
  \newline
}

% color pallet
\definecolor{C1}{HTML}{0B9F83}
\definecolor{C2}{HTML}{42858B}
\definecolor{C3}{HTML}{786C93}
\definecolor{C4}{HTML}{AF529B}
\definecolor{C5}{HTML}{E639A3}

%%%%%
% note that the opacity creates the two colors
% in the tcolorbox
%%%%%

% $1:= Title
% $2:= Color
\newenvironment{cvsection}[2] {
  \begin{tcolorbox}[
    standard jigsaw, % make background transparent
    opacityback=0,   % make background transparent
    top=0mm,         % size of top boarder
    bottom=0mm,      % size of bottom boarder
    boxrule=0pt,     % boarder of sort
    enhanced,        % enable frame code
    frame code={
      \path[draw=#2,line width=3pt]
        (frame.south west) --
        ([yshift=-0.29cm] frame.north west) --
        ([yshift=-0.29cm, xshift=0.2\linewidth] frame.north west);
    }
  ]
  \hspace{0.19\linewidth}
  \textbf{\texttt{\Large{#1}}}
  \large
  \vspace{5pt}
  \newline
}
{ \end{tcolorbox} }

\newenvironment{tightemize}
{\vspace{-2pt}\begin{itemize}[leftmargin=*]\itemsep1pt \parskip0pt \parsep0pt}
{\end{itemize}}

\newcommand{\HRule}[2]{\textcolor{#1}{\rule{\linewidth}{#2}}}
\newcommand{\header}[1]{{\large\textbf{#1}}\newline}
\newcommand{\locationdate}[2]{\textit{#1} \hfill \textit{#2}}
\newcommand{\spacer}{\quad}

\begin{document}
\thispagestyle{empty}
\begin{center}
{ \huge \bfseries Samuel Weitzman}\\[0.2cm]
\foreach \x in {C5, C4, C3, C2, C1} {%
  {\color{\x}\rule{.1\textwidth}{0.6pt}}%
}\\
{\Large
  {\textcolor{black!75}{\large\faPhone}}\ \texttt{774.218.5184}\spacer
  {\textcolor{black!75}{\large\faEnvelope}}\ \texttt{sameweitzman@gmail.com}\spacer\\
  {\textcolor{black!75}{\large\faLinkedin}}\ \href{linkedin.com/in/seweitzman}{\texttt{linkedin.com/in/seweitzman}}\spacer
  {\textcolor{black!75}{\large\faGithub}}\ \href{githhub.com/my_github_page}{\texttt{github.com/sweitzma}}\\
  % {\large\faHome}\5\href{mypersonalwebsite.com}{mypersonalwebsite.com}\\
}
\foreach \x in {C5, C4, C3, C2, C1} {%
  {\color{\x}\rule{.17\textwidth}{0.6pt}}%
}
\end{center}

\begin{minipage}[t][0.8\textheight]{.27\textwidth}
\vspace{1pt}
\begin{cvsection}{languages}{C1}
Ruby\skill{4}
Python\skill{3}
SQL\skill{2}
JavaScript\skill{2}
Bash\skill{2}
\TeX\skill{2}
HTML/CSS\skill{2}
\end{cvsection}
\vfill
\begin{cvsection}{skills}{C3}
  Web Dev\skill{3}
  Data Science\skill{2}
  Data Eng\skill{2}
  SRE\skill{1}
  DevOps\skill{1}
\end{cvsection}
\vfill
\begin{cvsection}{tools}{C5}
Rails\skill{4}
Git\skill{4}
Vim\skill{4}
Docker\skill{3}
Postgres\skill{3}
AWS\skill{2}
React\skill{2}
Terraform\skill{1}
\end{cvsection}
\vfill
\end{minipage}
\hfill
\begin{minipage}[t][0.8\textheight]{.7\textwidth}
\vspace{1pt}
\begin{cvsection}{work - \href{https://meraki.cisco.com/}{cisco meraki}}{C1}
  \header{Insights Team}
  \locationdate{Software Engineer}{Oct. 2019 - Present}
  \begin{tightemize}
    \item Worked everywhere from data science, data engineering, backend, and frontend.
    \item In a small team developed a Bayesian anomaly detection system for network degradation performance alerts.
  \end{tightemize}

  \vspace{10pt}

  \header{Switching Team}
  \locationdate{Software Engineer}{Sep. 2018 - Oct. 2019}
  \begin{tightemize}
  \item Full stack role working mainly with Ruby on Rails.
    \item Focused on feature building, bug fixing, code quality, scalability.
    \item One of 3 people for a Switch dashboard supporting over 600,000 customer networks and millions of pageviews per week.
  \end{tightemize}
  \ 
\end{cvsection}
\vfill
\begin{cvsection}{education - \href{https://www.brown.edu/}{brown university}}{C3}
  \header{B.Sc. Mathematics - Computer Science}{}
  \locationdate{Providence, RI}{Sep. 2014 - May 2018}\\
  \locationdate{GPA: 4.00}{}\\
  Diverse undergrad education specializing in topics at the intersection of theoretical math, applied math, and computer
  science.\\
\end{cvsection}
\vfill
\begin{cvsection}{about me}{C5}
  Originally from MA, I currently live in San Francisco.
  I enjoy helping people, both through my work and the people immediately around me.
  I value intentional design and lifelong learning.
  Outside of tech my interests include sustainable agriculture, trail running, and fermented foods.\\
\end{cvsection}
\vfill
\end{minipage}
\end{document}
